
\documentclass[11pt,a4paper,twoside]{report}

\newcommand{\bosonsampling}{\textsc{BosonSampling}}
\newcommand{\rstar}{R^{*}}
\newcommand{\pt}{\(\mathcal{PT}\)}
\newcommand{\mat}[1]{\mathrm{#1}}

\begin{document}

\chapter{The Last Bulk Optics Experiment}
\label{ch:BulkCircuit}

\section{Introduction}
In this chapter, I describe the calibration and testing of a completely
reconfigurable circuit in bulk optics. By altering the parameters in this single
experiment, we were able to simulate the action of any lossless linear optics
circuit on four modes. The architecture was motivated by (but not identical to)
the scheme described by Reck et al in \cite{reck94}. An application of this
circuit to quantum simulation is described in chapter~\ref{ch:Simulations}.

\section{Calibration (the crapusoids are real)}

\section{Benchmarking (arguably the first boson sampler)}

\chapter{Direct Dialling}
\label{ch:DirectDialling}

Early theoretical work that I did. Motivated by the question: if we want a Haar
unitary from a Reck scheme\cite{reck94}, can we just set the parameters
(reflectivities and phase shifts) randomly and independenly? If so, what
distributions? Answer: yes and a load of beta distributions, depending on where
the beamsplitter is.

\section{Arithmetic of probability density functions}
I spent a lot of time considering these. I think I can present this as
preliminary material.

\section{The Reck scheme}
More background. Essential for several sections/chapters.

\section{Results: the distributions}
Explicitly lay out what probability distributions are required.

\section{Proof}
In terms of a coordinate transformation

\section{Applications}
Most obviously, generating Haar unitaries (or truncations thereof) directly in
experimental parameters

Further work: reconstructing a unitary using Bayesian inference on this
parameterisation.

\chapter{Boson simulations (it's just diagonalisation)}
\label{ch:Simulations}

This formed the bulk of the experimental work in my PhD. Roughly speaking, we
take a hamiltonian, \(\mat{H}\) and exponentiate it to get a load of unitaries
(\(\mat{U}=e^{-i\mat{H}t}\)) at a series of timesteps. Using a decomposition
similar to the one in \cite{reck94} we can implement these on a single
circuit.

Two physical implementations: bulk optics and integrated optics. I was
responsible for the calibration of the bulk circuit (crapusoids), writing the
control code, and taking a large portion of the data. I trained DTC student
Chris Sparrow in the operation of the experiment.

\section{Molecular vibrations}
Simulating phonons in the harmonic limit corresponds to vibrations of molecules.

\section{\pt-symmetric systems}
Taking a non-Hermitian hamiltonian, \(\mat{G}\) corresponds to an open system
with loss and/or gain. A system with balanced but spatially separated loss and
gain is \pt-symmetric. Exponentiating this hamiltonian gives us a non-unitary
time-evolution operator, \(\mat{V}\). Using unitary dilation, we implement this
as a sub-matrix of a unitary operator. Physically, this correspods to coupling
the system to an environment with an equal number of spatial modes.

\chapter{Verification}
\label{ch:Verification}

Work relating to verification in quantum walks and \bosonsampling. I don't think
it's unfair to say that I had the original motivation to implement the
\(\rstar\) protocol described in \cite{aaronson13}. I did the Bayesian model
comparison between \bosonsampling and uniform distributions.

\chapter{Tomography of Hamiltonians (just take the time derivative)}
\label{ch:Hamiltomo}
The hamiltomo project. Using super-stable tomography, we can measure the unitary
description of a photonic device. If the unitary is generated by a time-constant
Hamiltonian (as in quantum walks) then successive measurements of \(\mat{U}\)
(at least 2) can be used to reconstruct the underlying Hamiltonian. Use the time
derivative method.

\chapter{Decoupling}
\label{ch:Decoupling}

Project with Pete Turner.

\bibliographystyle{abbrv}
\bibliography{bib/thesis}

\end{document}
