\chapter{Publications and Presentations}
\label{app:publications}
I have been co-author on the following papers, which have been published or
accepted for publication:
\begin{itemize}
  \item J. Carolan, J. D. A. Meinecke, P. J. Shadbolt, N. J. Russell, N. Ismail,
    K. W\"orhoff, T. Rudolph, M. G. Thomson, J. L. O'Brien, J. C. F. Matthews
    and A. Laing, ``On the experimental verification of quantum complexity in
    linear optics'', \textit{Nat Photon, 8(8):621-626}, August 2014. Article.
  \item J. Carolan, C. Harrold, C. Sparrow, E. Mart\'in-L\'opez, N. J. Russell,
    J. Silverstone, P. Shadbolt, N. Matsuda, M. Oguma, M. Itoh, G. Marshall, M.
    G. Thomson, J. C. F. Matthews, T. Hashimoto, J. L. O'Brien and A. Laing,
    ``Universal Linear Optics'', \textit{arXiv:1505.01182 [quant-ph]}, May 2015.
    Accepted for publication in Science June 2015.
\end{itemize}
In addition, I am first author of the following preprints, of which one appears
on the arXiv and the other two are in preparation:
\begin{itemize}
  \item N. J. Russell, J. L. O'Brien and A. Laing, ``Direct dialling of Haar
    random unitary matrices'', \textit{arXiv:0506.06220 [quant-ph]}, June 2015.
  \item N. J. Russell, J. Y. Joglekar, C. Sparrow, C. Harrold, J. L. O'Brien and
    A. Laing, ``\(\mathcal{PT}\)-symmetric systems: quantum simulation and
    correlations'', \textit{in preparation}.
  \item N. J. Russell, J. Carolan, C. Harrold, J. L. O'Brien and A. Laing,
    ``Efficient tomography of Hamiltonians'', \textit{in preparation}.
\end{itemize}
I am co-author on one additional preprint
\begin{itemize}
  \item E. Mart\'in L\'opez, N. J. Russell, C. Sparrow, J. L. O'Brien and A.
    Laing, ``Quantum simulation of phonons in the harmonic limit'',
    \textit{in preparation}.
\end{itemize}
I have given the following conference presentations, listed in chronological
order; individual entries indicate whether the presentation was a talk or
poster.
\begin{itemize}
  \item ``Efficient quantum process tomography of linear optical devices'',
    QCMC, Hefei University China, November 2014 (poster).
  \item ``Efficient quantum process tomography of linear optical devices'',
    Photon14, Imperial College London, September 2014 (talk).
  \item ``Direct dialling of Haar unitary matrices in linear optics'', Photon14,
    Imperial College London, September 2014 (poster).
  \item ``Quantum simulation of non-interacting bosons'', University of Bristol
    postgraduate conference, University of Bristol, June 2013 (talk).
  \item ``Architectures for a linear-optical quantum computer'', QuICC workshop,
    Aberystwyth University, August 2012 (talk).
  \item ``Experimental realisation of any unitary operator'', QuICC workshop,
    Aberystwyth University, August 2012 (poster).
\end{itemize}
In addition, I have been invited to give a talk about my research at external
seminars on the following occasions
\begin{itemize}
  \item ``Efficient quantum process tomography of linear optical devices'',
    MIT, March 2015.
  \item ``Verification in non-universal quantum computing'', Xi'an Jiaotong
    University China, November 2014.
\end{itemize}
